Towards Verified Time Balancing of Security Protocols

### 2019-01-20 Src/talk.tex
some more changes to talk

\begin{frame}[fragile]
  \frametitle{Building a type of Prg n}
  \begin{table}[h!]
  \begin{tabular}{c|c|c|c}
  Statement & Continuation & Result & Description \\
  \hline 
  Halt & - & Prg 1 & Terminate \\
  AssC & Prg k & Prg (k + 1) & Asn constant. \\
  AssV & Prg k & Prg (k + 1) & Asn variable. \\
  UnOp & Prg k & Prg (k + 1) & Asn result of unary op. \\
  BinOP & Prg k & Prg (k + 1) & Asn result of binary op. \\
  Do & Prg k & Prg (m * n + k) & Run Prg m, n times. \\
  Cond & Prg k & Prg (n + k) & Branch on Prg n. \\
  Skip & Prg k * Prg (k + 1) & Do Nothing.
  \end{tabular} 
  \end{table}
  Conditionals require both branches to be Prg n. Ensuring
  That all branches of the program are correct by construction.
\end{frame}

>>>>

\begin{frame}[fragile]
  \frametitle{Correctness by construction}
  \begin{itemize}
    \item The protocol implementations can be
          quite complex, possibly giving rise
          to equally complex proof obligations.
    \item We'd like to reduce this burden somehow!
    \item We can design a language that is just 
          big enough to compute what we like, 
          but restrictive enough to capture the
          invariants we care about.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Building a type of Prg n}
  \begin{table}[h!]
  \begin{tabular}{c|c|c|c}
  Statement & Continuation & Result & Description \\
  \hline 
  Halt & - & Prg 1 & Terminate \\
  AssC & Prg k & Prg (k + 1) & Asn constant. \\
  AssV & Prg k & Prg (k + 1) & Asn variable. \\
  UnOp & Prg k & Prg (k + 1) & Asn result of unary op. \\
  BinOP & Prg k & Prg (k + 1) & Asn result of binary op. \\
  Do & Prg k & Prg (m * n + k) & Run Prg m, n times. \\
  Cond & Prg k & Prg (n + k) & Branch on Prg n. \\
  Skip & Prg k & Prg (k + 1) & Do Nothing.
  \end{tabular} 
  \end{table}
  Conditionals require both branches to be Prg n. Ensuring
  That all branches of the program are correct by construction.
\end{frame}
